\documentclass{article}
\title{High Level Customer User Stories}
\author{Syeda Noor Jaha Azim}
\date{January 30, 2018}
\begin{document}
\maketitle

\section{Epic : }
As a user I would like to have an option to search for books with any possible criteria and see all the details of the book I choose. I should be able to look for the convenient booksellers in terms of availability and price of the book. I would also like suggestions on books that matches my reading choice. So that it is easy for me to find the book I want and purchase it from the convenient bookseller. 

\section{User Stories : }
\subsection{Search Books}
As a Customer, I want to search for books so that I can see the book’s details.
\linebreak
\linebreak
 A search form with the following fields :
\begin{enumerate}
	\item[--] Author
	\item[--] Title
	\item[--] Genre
	\item[--] Price range
	\item[--] Rating
	\item[--] Number of pages
	\item[--] Publisher
	\item[--] Publication Year
\end{enumerate}

\subsection{Compare Booksellers}
As a Customer, I want to look for convenient booksellers with the book I am searching for, so that I can easily visit the bookseller’s website.
\linebreak
\linebreak
A list of all the booksellers with the following details :
\begin{itemize}
	\item  Name of bookseller
	\item Price including shipping cost
	\item Availability of the book (such as number of books, number of shipping days or location of bookstore)
	\item  Hyperlink that navigates to the bookseller’s website
\end{itemize}

\subsection{Recommend Books}
As a Customer I want suggestion on books so that I can easily find the books that matches my reading choice.

\subsection{Regular User}
As a regular user I want to update my book preferences so that I get suggestion for books according to my updated preference.

\subsection{Authorized User}
As a user I want to rate books and update my preferences and make sure no one can see my profile so that I can keep privacy of my book choice.

\subsection{Sort Books}
As a user I want an option that will sort the book list according to publication Year or page number so that I can easily skip through the list of books.


\end{document}